---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiltPlot

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/2DegreesInvesting/tiltPlot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/tiltPlot/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/2DegreesInvesting/tiltPlot/branch/main/graph/badge.svg)](https://app.codecov.io/gh/2DegreesInvesting/tiltPlot?branch=main)
<!-- badges: end -->

The goal of tiltPlot is to provide plots for the TILT project. 

## Example

Let us load the toy data set.

```{r}
library(tiltPlot)
```

### 1. Sankey Plot 

```{r}
sankey_toy_data
```


Here is the default Sankey Plot. By default the function plots with companies and uses an "equal_weight" mode.

```{r}
plot_sankey(sankey_toy_data)
```


You can also choose to have the plot without the company node.

```{r}
plot_sankey(sankey_toy_data, with_company = FALSE)
```

Finally, the user can choose different modes to plot the Sankey plot if financial data
is available.

```{r eval=interactive()}
plot_sankey(sankey_toy_data, with_company = FALSE, mode = "best_case")
```

### 2. XCTR plot for one company

```{r}
xctr_toy_data
```

```{r}
plot_xctr_company_level(xctr_toy_data, "company_a")
```

### 3. XCTR plot on the portfolio level

```{r}
plot_xctr_portfolio_level(xctr_toy_data)
```


