---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiltPlot

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/2DegreesInvesting/tiltPlot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/tiltPlot/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/2DegreesInvesting/tiltPlot/branch/main/graph/badge.svg)](https://app.codecov.io/gh/2DegreesInvesting/tiltPlot?branch=main)
<!-- badges: end -->

The goal of tiltPlot is to provide plots for the TILT project.

## Installation

You can install the development version of tiltPlot from GitHub with:

```r
# install.packages("pak")
pak::pak("2DegreesInvesting/tiltPlot")
```

## Example

```{r}
library(ggplot2)
library(dplyr, warn.conflicts = FALSE)
library(tiltPlot)
```

### 1. Sankey Plot with financial data

```{r}
financial
```

Here is the default Sankey Plot. By default the function plots with companies and uses an "equal_weight" mode.

```{r}
fin <- financial
plot_sankey(fin)
```

You can also choose to have the plot without the company node.

```{r}
plot_sankey(fin, with_company = FALSE)
```

Finally, the user can choose different modes to plot the Sankey plot with financial data available.

```{r}
plot_sankey(fin, with_company = FALSE, mode = "best_case")
```

### 2. XCTR plots with financial data

```{r}
financial
```

On a company level:

```{r}
fin <- financial

plot_xctr_financial(fin, "peter", mode = "worst_case") +
  labs(title = "Risk distribution of all products on a company level, on a financial weight")
```

On a portfolio level:

```{r}
plot_xctr_financial(fin, mode = "worst_case") +
  labs(title = "Risk distribution of all products on a portfolio level, on a financial weight")
```


### 3. XCTR plots without financial data

```{r}
without_financial
```

Plot on a company level.
The user can choose any number of benchmark to be plotted. 
If the benchmarks argument is not given to the function, the function will plot 
all the benchmarks.

```{r}
no_fin <- without_financial

benchmarks <- c("all", "unit", "isic_sec")

no_fin |>
  filter(company_name == "peter") |>
  bar_plot_xctr(benchmarks) +
  labs(title = "Emission profile of all products on a company level")
```

Plot on a portfolio level. 

```{r}
bar_plot_xctr(no_fin, benchmarks) +
  labs(title = "Emission profile of all products on a portfolio level")
```

### 4. Create a German map with risk categories color gradient

```{r}
map_region_risk(financial, "DE", benchmark = "unit_isic_sec") +
  labs(title = "German map of high, medium and low propotion of the companies
  that are found in one region.
  © EuroGeographics for the administrative boundaries ")
```



